RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-12-03 manuscripts/manuscript.Rmd
update supertreebase URL, closes #102

```{r eval=FALSE}
tb_nex <- nexml_read("https://raw.github.com/rvosa/supertreebase/master/data/treebase/S100.xml")
tb_phy <- get_trees_list(tb_nex)
plot(tb_phy[[1]])
```

>>>>

```{r eval=FALSE}
tb_nex <- nexml_read("https://raw.github.com/TreeBASE/supertreebase/master/data/treebase/S100.xml")
tb_phy <- get_trees_list(tb_nex)
plot(tb_phy[[1]])
```
